---
title: "Título"
author: Sergio Uribe
date: "`r format(Sys.time(), '%d %B, %Y')`"

output: 
  html_notebook: 
    toc: yes
    toc_float: true
    fig_caption: true
---

# Shortcuts
Cmd/Ctrl + Shift + C for (un)commenting

Cmd/Ctrl + Shift + M for adding `%>%`
Cmd/Ctrl + I for auto-indentation

Alt + Up or Down to move current line(s) without copying and pasting

Cmd + Option + Up or Down / Shift + Alt + Up or Down to insert a copy of current line(s) 

F7 for spell check
Ctrl + Shift + 1-4  expands the different panes into full view in RStudio :)

# Load packages
if (!require("gapminder")) install.packages("gapminder") #instala paquetes en caso que no estén instalados



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```



# fake data https://github.com/ropensci/charlatan

# turn off scientific notation
 options(scipen = 999) 

# Paquetes
```{r, include = F, echo = F}
Packages <- c("tidyverse", "forcats", "stringr", "broom")
lapply(Packages, library, character.only = TRUE)
rm(Packages)
```

#EDA


---------------------------------------------
## EDA by https://blog.datascienceheroes.com/exploratory-data-analysis-in-r-intro/
library(funModeling) 
library(tidyverse) 
library(Hmisc)

basic_eda <- function(data)
{
  glimpse(data)
  df_status(data)
  freq(data) 
  profiling_num(data)
  plot_num(data)
  describe(data)
}

basic_eda(my_amazing_data)
---------------------------------------------


# Remueve columnas con cierto nivel de NA
x <- df[ lapply( df, function(x) sum(is.na(x)) / length(x) ) < 0.4 ]


https://blog.datascienceheroes.com/exploratory-data-analysis-data-preparation-with-funmodeling/
funModeling # data preparation, profiling, selecting best variables 'dataViz', 

install.packages("visdat")

https://infer.netlify.com/

ggally http://ggobi.github.io/ggally/#ggally

devtools::install_github("ThinkR-open/remedy") #provides addins to facilitate writing in markdown with RStudio.
library(remedy)

install.packages("citr") # citas

Otros paquetes

ggthemeassist # provides a GUI for editing ggplot2 themes
ggplotAssist #addin for teaching and learning making plot using the 'ggplot2' 
dplyrAssist #addin for teaching and learning data manipulation using the 'dplyr' package
assessing model performance and other functions. (ver en http://bit.ly/2DAiGmJ ) 
gghighlight: Highlight ggplot's Lines and Points with Predicates

epitool #Tools for training and practicing epidemiologists including methods for two-way and multi-way contingency tables.
pubh #PublicHealth (ver https://cran.rstudio.com/web/packages/pubh/vignettes/introduction.html) 

Otros

## Modelling 


https://github.com/vincentarelbundock/gtsummary Varios modelos en una tabla


https://github.com/WinVector/vtreat
vtreat is an R data.frame processor/conditioner that prepares real-world data for predictive modeling in a statistically sound manne

FINALFIT http://www.datasurg.net/2018/05/16/elegant-regression-results-tables-and-plots-the-finalfit-package/ 

### Check interations
https://interactions.jacob-long.com/index.html

wordcountaddin # cuenta palabras no code

install.packages("datapasta") #copiar y pegar tablas, ver https://github.com/MilesMcBain/datapasta


# install.packages("devtools") devtools::install_github("sicarul/xray") 


ver https://livebook.datascienceheroes.com/

Plots
```{r, include = F, echo = F}
install.packages("devtools")

devtools::install_github("gertstulp/ggplotgui")
devtools::install_github("LudvigOlsen/splitChunk") #splitchunks
devtools::install_github("ropenscilabs/skimr") # summary stats

library("ggplotgui")
```

#Recrear datos
library(splitstackshape)
expandRows(data.frame(as.table(originalTable)), "Freq")


### Lineas de significancia para los gráficos

install.packages("ggsignif")
library(ggsignif)


# Dataset

## Data cleaning
```{r janitor}
library(janitor)

df_clean - df_dirty %>% 
        clean_names() %>%
        remove_empty_rows() %>% 
        remove_empty_cols() 
```

### Search & replace
df <- dplyr::mutate_if(tibble::as_tibble(df), 
                                is.character, 
                                stringr::str_replace_all, 
                       pattern = "oldVar",replacement = "newVar")

## Dataset clean

vis_dat(df)

# Exploratory Data Analysis

# Inferential Analysis

# Citas

```{r}
citation()
citation(package = "tidyverse")
citation(package = "stringr")
citation(package = "broom")
citation(package = "editData")
```
